Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-09-23 sections/srfm.tex
some closing remarks on the section of SMLM.

The resolution provided by this approach scales with the number of photons $N$
that are detected and theoretically is given by $\sigma_\text{PSF}/\sqrt{N}$
(with $\sigma_\text{PSF}$ denoting the standard deviation of the point spread
function of the microscope, which is in the range of 100\,nm). However, in
practice the resolution is range of 20\,nm \cite{Betzig2006} since the
theoretical resolution cannot be reached due to background, noise and other
factors. A more detailed description of the resolution enhancement by
localisation is provided by \cite{Mortensen2010}.

\subsubsection{Deterministic approaches}
\label{sec:deterministic-approaches}

>>>>

The resolution provided by this approach scales with the number of photons $N$
that are detected and theoretically is given by $\sigma_\text{PSF}/\sqrt{N}$
(with $\sigma_\text{PSF}$ denoting the standard deviation of the point spread
function of the microscope, which is in the range of 100\,nm). However, in
practice the resolution is in the range of 20\,nm \cite{Betzig2006,Rust2006}
since the theoretical resolution cannot be reached due to background, noise
and other factors. A more detailed description of the resolution enhancement
by localisation is provided by \cite{Mortensen2010}.

This brief explanation is far from being exhaustive and does not consider the
differences in the implementations of the various techniques. An in-depth
overview is provided by several reviews of the techniques
\cite{Sengupta2014,Liu2015,Sauer2017}, suitable dyes \cite{Li2018a} as well
as by detailed imaging protocols \cite{Gould2009,Schermelleh2010,Linde2011}.
\subsubsection{Deterministic approaches}
\label{sec:deterministic-approaches}
